---
title: "LongitudinalMycobiome"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

clean enrivronment
```{r}
rm(list = ls())
```

Import required packages
```{r packages}
library(ggpubr)
library(patchwork)
library(tidyverse)
library(phyloseq)
library(ggplot2)
library(reshape2)
library(nlme)
library(compositions)
library(vegan)
library(phyloseq)
library("ape")
library(microbiome)
library(dplyr)
library(psych)
```

Define functions
```{r}
import_buglist_phyloseq <- function(path_buglist, path_metadata, delimiter) {
 library(phyloseq)
 buglist <- read.csv(path_buglist,header = T, sep = delimiter, row.names = 1, check.names = F)
 buglist[is.na(buglist)] <- 0
 metadata <- read.csv(path_metadata, header = T, sep = delimiter,row.names = 1,check.names = F)
 metadata[is.na(metadata)] <- "NA"
 rm(buglist_species)
 buglist_species <- extract_species(buglist)
 buglist_species <- buglist_species %>%  sweep(2,colSums(.),"/")
 buglist_species <- buglist_species*100
 rm(taxa_table)
 taxa_Table <- extract_taxaTable(buglist_species)
 phy_species <- import_phyloseq(buglist_species,taxa_Table,metadata)
 return(phy_species)
}
import_pwylist_phyloseq <- function(path_pwylist, path_metadata, delimiter){
 library('phyloseq')
 pwylist <- read.csv(path_pwylist,header = T, sep = delimiter, row.names = 1, check.names = F)
 pwylist[is.na(pwylist)] <- 0
 metadata <- read.csv(path_metadata, header = T, sep = delimiter,row.names = 1,check.names = F)
 metadata[is.na(metadata)] <- "NA"
 sampdata <- sample_data(metadata)
 ptable <- otu_table(pwylist, taxa_are_rows = T)
 phy_protein <- phyloseq(ptable, sampdata)
 random_tree = rtree(ntaxa(phy_protein), rooted=TRUE, tip.label=taxa_names(phy_protein))
 phy_protein = merge_phyloseq(phy_protein, sampdata, random_tree)
 return(phy_protein)
}
extract_species <- function(buglist){
 to_look = "s__"
 for (i in row.names(buglist)) {
  if (grepl(to_look,i)) {
   if (!exists("just_species")){
    just_species <- data.frame(buglist[i,],check.names = F)
   } 
   else if (exists("just_species")){
    just_species <- rbind(just_species, buglist[i,])
   }
  }
 }
 just_species[is.na(just_species)] <- 0
 return(just_species)
}
extract_taxaTable <- function(only_species){
 library(stringr)
 library(phyloseq)
 for (i in row.names(only_species)) {
  tax_list <- str_split(i,"\\|", simplify = T)
  kingdom <- str_split(tax_list[1], pattern = "k__", simplify = T)[2]
  phylum<- str_split(tax_list[2], pattern = "p__", simplify = T)[2]
  class<- str_split(tax_list[3], pattern = "c__", simplify = T)[2]
  order<- str_split(tax_list[4], pattern = "o__", simplify = T)[2]
  family<- str_split(tax_list[5], pattern = "f__", simplify = T)[2]
  genus <- str_split(tax_list[6], pattern = "g__", simplify = T)[2]
  specie <- str_split(tax_list[7], pattern = "s__", simplify = T)[2]
  
  if (!exists("taxa_table")){
   taxa_table <- data.frame(kingdom, phylum, class, order, family, genus, specie, stringsAsFactors = F)
  } 
  else if (exists("taxa_table")){
   taxa_table <- rbind(taxa_table, c(kingdom, phylum, class, order, family, genus, specie))
  }
 }
 row.names(taxa_table) <- row.names(only_species)
 return(taxa_table)
}
import_phyloseq <- function(only_species,tax,meta){
 library(phyloseq)
 tax = tax_table(tax)
 colnames(tax) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")
 taxa_names(tax) <- row.names(only_species)
 otable <- otu_table(only_species,taxa_are_rows = T)
 mdata <- sample_data(meta)
 phyObject <- phyloseq(otable, mdata, tax)
 random_tree = rtree(ntaxa(phyObject), rooted=TRUE, tip.label=taxa_names(phyObject))
 phyObject = merge_phyloseq(phyObject,random_tree)
 return(phyObject)
}

residual_Eadjusted <- function(table){
  Residual_adjusted_table <- matrix(nrow=nrow(table), ncol=ncol(table))
  for (i in 1:nrow(table)){
    linear<-lm(as.numeric(table[i,])~as.numeric(table[1,]))
    Residual_adjusted_table[i,]<-linear$residuals+ mean(as.numeric(table[i,]))
  }
  colnames(Residual_adjusted_table)<- colnames(table)
  rownames(Residual_adjusted_table)<-rownames(table)
  Residual_adjusted_table <- Residual_adjusted_table[-1,]
  return(Residual_adjusted_table)
}

density_Eadjusted <- function(table){
  Density_adjusted_table <- matrix(nrow=nrow(table), ncol=ncol(table))
  Density_adjusted_table <- table/table[1,]*100
  Density_adjusted_table <- Density_adjusted_table[-1,]
  return(Density_adjusted_table)
}

wilcoxon_calculate <- function(table1, table2){
  pval_wilcoxon <- matrix(ncol=1, nrow=nrow(table1))
  for (i in 1:nrow(table1)) {
    t <- wilcox.test(table1[i,],table2[i,])
    pval_wilcoxon[i,1] <- t$p.value
  }
  rownames(pval_wilcoxon) <- rownames(table1)
  colnames(pval_wilcoxon) <- "Wilcoxon pval"
  return(pval_wilcoxon)
}
icc_calculate <- function(table1, table2){
  icc.table <- matrix(ncol=1, nrow=nrow(table1))
  for (i in 1:nrow(table1)){
    corr_table1 <- data.frame(table1[i,], table2[i,])
    icc1<-ICC(corr_table1)
    icc.table[i,1]<-icc1$results$ICC[3]
  }  
  rownames(icc.table) <- rownames(table1)
  colnames(icc.table) <- "ICC number"
  return(icc.table)
}
```

Import buglists and metadata
```{r just_species}
####### TAXA #######
myco_phy_all <- import_buglist_phyloseq(path_buglist = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/ANALYSIS/buglists_link/all_buglist.txt",path_metadata = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/metadata.csv",delimiter = '\t')
myco_phy_common <- import_buglist_phyloseq(path_buglist = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/ANALYSIS/buglists_link/merged_common_buglist.txt",path_metadata = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/metadata.csv",delimiter = '\t')
myco_phy_fungi <- import_buglist_phyloseq(path_buglist = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/ANALYSIS/buglists_link/fungi_buglist.txt",path_metadata = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/metadata.csv",delimiter = "\t")
metadata_lm <- read.csv("/mnt/synology/ZIXUAN/LongitudinalMycobiome/metadata.csv",header = T,row.names = 1,sep = "\t")
# ffq <- read.csv("/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/FFQnutrients_LongitudinalMycobiome.tsv",header = T,sep = '\t',row.names = 1,check.names = F)
# foods <- read.csv("/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/dailyintake_LongitudinalMycobiome_classified.csv",header = T,sep = '\t',row.names = 1)
# ffq1 <- ffq[ffq$sFFQ=="1",-34]
# ffq2 <- ffq[ffq$sFFQ=="2",-34]
# foods1 <- foods[-25,foods[25,]=="1"]
# foods2 <- foods[-25,foods[25,]=="2"]
# merged_fd <- (foods1+foods2)/2
# rm(ffq1,ffq2,foods1,foods2)
# 
# write.csv(ffq,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/ffq_merged.csv",row.names = T)
# write.csv(merged_fd,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/foods_merged.csv",row.names = T)

####### FUNC #######
pwy_list <- read.csv("/mnt/synology/ZIXUAN/LongitudinalMycobiome/ANALYSIS/pwy_link/merged_common_pwy_unstratified.txt",sep = '\t',header = T,row.names = 1,check.names = T)
func_phy <- import_pwylist_phyloseq(path_pwylist = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/ANALYSIS/pwy_link/merged_common_pwy_unstratified.txt",path_metadata = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/metadata.csv",delimiter = "\t")
func_phy_fungi <- import_pwylist_phyloseq(path_pwylist = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/ANALYSIS/pwy_link/fungi_pwy_unstratified.txt",path_metadata = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/metadata.csv",delimiter = "\t")
```

Energy Adjustment
```{r}
ffq1 <- t(ffq1)
ffq2 <- t(ffq2)
#### residual method
Residual_adjusted_ffq1 <- residual_Eadjusted(table = ffq1)
Residual_adjusted_ffq2 <- residual_Eadjusted(table = ffq2)

adjusted_ffq <- (Residual_adjusted_ffq1+Residual_adjusted_ffq2)/2
colnames(adjusted_ffq) <- c("L1","L2","L3","L4","L5","L6")
write.csv(adjusted_ffq,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/Res_adj_ffq_merged.csv",row.names = T)

#### density method
Density_adjusted_ffq1 <- density_Eadjusted(table = ffq1)
Density_adjusted_ffq2 <- density_Eadjusted(table = ffq2)

```

Compare two sFFQs
  two sFFQs are not significantly different with each other
```{r}
#### Wilcoxon
pval_wcx_ffq <- wilcoxon_calculate(table1 = Residual_adjusted_ffq1, table2 = Residual_adjusted_ffq2)
pval_wcx_fd <- wilcoxon_calculate(table1 = t(t(foods1)), table2 = t(t(foods2)))


#### ICC 
icc_ffq <- icc_calculate(table1 = Residual_adjusted_ffq1, table2 = Residual_adjusted_ffq2)
icc_fd <- icc_calculate(table1 = t(t(foods1)), table2 = t(t(foods2)))
write.csv(pval_wcx_ffq,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/pval_wcx_ffq.csv",row.names = T)
write.csv(pval_wcx_fd,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/pval_wcx_fd.csv",row.names = T)
write.csv(icc_ffq,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/icc_ffq.csv",row.names = T)
write.csv(icc_fd,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/sFFQ_diet/icc_fd.csv",row.names = T)
```

Make subset phyloseq
```{r}
subset <- subset_samples(myco_phy_fungi)
# subset <- subset_samples(myco_phy_fungi,Gender=="Male")
# subset <- subset_samples(fung_phy, study=="metahit_spain188")
subset_metadata <- data.frame(sample_data(subset))
# subset_metadata$BMI <- as.numeric(subset_metadata$BMI)
# subset_metadata$Host_Age <- as.numeric(subset_metadata$Host_Age)
subset_otu <- data.frame(otu_table(subset))
subset_otu <- subset_otu %>%
  mutate_if(is.numeric,round)
subset_otu <- subset_otu[colSums(subset_otu) > 0]
subset_otu <- subset_otu[rowSums(subset_otu) > 0,]
otable <- otu_table(subset_otu,taxa_are_rows = T)
mdata <- sample_data(subset_metadata)
phyloseq_sub <- phyloseq(otable,mdata)
random_tree = rtree(ntaxa(phyloseq_sub), rooted=TRUE, tip.label=taxa_names(phyloseq_sub))
phyloseq_sub = merge_phyloseq(phyloseq_sub, mdata, random_tree)
```

Beta diversity
  Beta diversity in all three partitions are not significantly different (TAXA)
  Partition, Gender, Timepoint significantly contribute to functional variation (Functional)
```{r PCoA}
library(ggbiplot)

wunifrac_dist = phyloseq::distance(func_phy, method="unifrac", weighted=T)
ordination = ordinate(func_phy, method="PCoA", distance=wunifrac_dist)
adonis_res <- adonis2(wunifrac_dist~sample_data(func_phy)$Partition)

adonis_res2 <- adonis2(wunifrac_dist~ sample_data(func_phy)$BirthType+sample_data(func_phy)$Timepoint+sample_data(func_phy)$Gender+sample_data(func_phy)$BMI+sample_data(func_phy)$IndividualID+sample_data(func_phy)$Partition)

#+ sample_data(phyloseq_sub)$Shannon_index + sample_data(phyloseq_sub)$Chao1_index


adonis_res2$variable = rownames(adonis_res2)
adonis_res2$FDR <- p.adjust(adonis_res2$`Pr(>F)`, method = "BH")
adonis_plot2 <- data.frame(adonis_res2[0:(nrow(adonis_res2)-2),])


ggplot(data = adonis_plot2, aes(x = R2, y = reorder(variable, - R2))) +
  geom_bar(stat = "identity") + 
  scale_x_continuous("Adonis R²") +
  theme_classic() + 
  ggtitle("Contribution of factors to data's functional effect size")


png("/home/zixuan/00-BACKUP/META/analysis/PCoA/fung_spain_wuni_0.03863383_0.004.png", units="in", width=10, height=7, res=300)


p <- plot_ordination(myco_phy_all, ordination, color="Partition") 
p + theme(aspect.ratio=1)+ theme_classic()+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2") +
  ggtitle("Pathways clustering (weighted unifrac)") +
  theme(plot.title = element_text(hjust = 0.5),text = element_text(size=30))+ 
  stat_ellipse(aes(fill = Partition), geom="polygon",level=0.95,alpha=0.2)

dev.off()

png("/home/zixuan/00-BACKUP/META/analysis/PCoA/fung_spain_bray_0.03088827_0.003.png", units="in", width=10, height=7, res=300)

phylo_ord2 <- ordinate(myco_phy, method = "PCoA", distance = 'bray')
p2 <- plot_ordination(myco_phy, phylo_ord2, color = "Partition")
p2 + theme(aspect.ratio=1)+ theme_classic()+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2") +
  ggtitle("Pathways clustering (bray-curtis)") +
  theme(plot.title = element_text(hjust = 0.5),text = element_text(size=30))+ 
  stat_ellipse(aes(fill = Partition), geom="polygon",level=0.95,alpha=0.2)

dev.off()

bl <- as.data.frame(t(subset_otu)) #the otu table for which you want to calculate

adonis_res <- adonis2(bl ~ disease, data = subset_metadata)

```

Plot alpha diversity
  Alpha diversity in fungi partition mycobiome is significantly higher than that in bacteria and control partitions
```{r dev='png',dpi=600}
library(easyGgplot2)
diversity_Shannon <- plot_richness(myco_phy_fungi,measures = "Shannon")$data
diversity_chao1 <- plot_richness(phyloseq_sub,measures = "Chao1")$data
diversity_obs <- plot_richness(phyloseq_sub,measures = "Observed")$data

png("/home/zixuan/00-BACKUP/META/analysis/DIVERSITY/bacteria/t2d_obs.png", units="in", width=8, height=5, res=300)
# tiff("E:/vhir/DB/analysis/DIVERSITY/T1D/china_T1D_shannon.tiff", units="in", width=10, height=7, res=300)
my_comparison=list(c("Fungi","Bacteria"),c("Fungi","Control"),c("Bacteria","Control"))

ggplot(diversity_Shannon,aes(x=reorder(Partition,value,na.rm=T),y=value)) + 
  geom_boxplot(width=0.5,lwd=1.5) +
  geom_jitter(width=0.3,aes(color=Partition)) +
  scale_color_brewer(palette="Dark2")+theme_classic()+
  theme(text = element_text(size=25),
        axis.text.x = element_text(angle=0, hjust=1)) +
  stat_compare_means(comparisons =  my_comparison)
dev.off()
```

Intra- and inter-individual dissimilarities
 bray-curtis dissimilarities intra group is not significantly lower than that of inter group (TAXA)
 bray-curtis dissimilarities intra group is significantly lower than that of inter group (FUNC)
```{r}
intra=c("L1","L2","L3","L4","L5","L6")
intra_dist <- vector(mode = "list")
for (i in intra) {
  subset <- subset_samples(func_phy, IndividualID==i)
  subset_otu <- data.frame(otu_table(subset))
  subset_metadata <- data.frame(sample_data(subset))
  subset_otu <- subset_otu[colSums(subset_otu) > 0]
  subset_otu <- subset_otu[rowSums(subset_otu) > 0,]
  otable <- otu_table(subset_otu,taxa_are_rows = T)
  mdata <- sample_data(subset_metadata)
  phyloseq_sub <- phyloseq(otable,mdata)
  random_tree = rtree(ntaxa(phyloseq_sub), rooted=TRUE, tip.label=taxa_names(phyloseq_sub))
  phyloseq_sub = merge_phyloseq(phyloseq_sub, mdata, random_tree)
  bray_dist=as.list(phyloseq::distance(phyloseq_sub, method="bray"))
  intra_dist=append(intra_dist,bray_dist)
}
intra_dist_num=as.numeric(na.omit(unlist(intra_dist)))
shapiro.test(intra_dist_num)

inter=c("T1","T2","T3","T4","T5","T6","T7","T8")
inter_dist <- vector(mode = "list")
for (t in inter) {
  subset <- subset_samples(func_phy, Timepoint==t)
  subset_otu <- data.frame(otu_table(subset))
  subset_metadata <- data.frame(sample_data(subset))
  subset_otu <- subset_otu[colSums(subset_otu) > 0]
  subset_otu <- subset_otu[rowSums(subset_otu) > 0,]
  otable <- otu_table(subset_otu,taxa_are_rows = T)
  mdata <- sample_data(subset_metadata)
  phyloseq_sub <- phyloseq(otable,mdata)
  random_tree = rtree(ntaxa(phyloseq_sub), rooted=TRUE, tip.label=taxa_names(phyloseq_sub))
  phyloseq_sub = merge_phyloseq(phyloseq_sub, mdata, random_tree)
  bray_dist=as.list(phyloseq::distance(phyloseq_sub, method="bray"))
  inter_dist=append(inter_dist,bray_dist)
}
inter_dist_num=as.numeric(na.omit(unlist(inter_dist)))
shapiro.test(inter_dist_num)
wilcox.test(intra_dist_num,inter_dist_num,alternative = "less")

intra_dist_num=data.frame(intra_dist_num)
intra_dist_num[,"group"]="intra"
inter_dist_num=data.frame(inter_dist_num)
inter_dist_num[,"group"]="inter"
colnames(intra_dist_num) <- c("dist","group")
colnames(inter_dist_num) <- c("dist","group")

plot.data <- rbind(intra_dist_num, inter_dist_num)

my_comparison=list(c("intra","inter"))

ggplot(plot.data,aes(x=reorder(group,dist,na.rm=T),y=dist)) + 
  geom_boxplot(width=0.5,lwd=1.5) +
  geom_jitter(width=0.3,aes(color=group)) +
  scale_color_brewer(palette="Dark2")+theme_classic()+
  theme(text = element_text(size=25),
        axis.text.x = element_text(angle=0, hjust=1)) +
  stat_compare_means(p.adjust.method = "bonferroni", comparisons =  my_comparison,
                     label = "p.signif", 
                     symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns")),
                     method.args = list(alternative = "less"))
```

Correlation between alpha diversity with nutrients
 The correlation between Birth type/Processed meet and alpha diversity is opposite to Fran's results
```{r}
write.csv(diversity_Shannon,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/TAXA/cor_AlphaD_METADATA/Shannong.csv")
diversity <- diversity_Shannon
####### Spearman and Pearson correlation #######
cor.personal.table <- matrix(ncol=4, nrow=2)
cor.nutrient.table <- matrix(ncol=4, nrow=32)
cor.foods.table <- matrix(ncol=4, nrow=24)
colnames(cor.nutrient.table) <- colnames(cor.personal.table) <- colnames(cor.foods.table) <- c("pval_P","cor_P","pval_S","cor_S")
j=1
for (i in c(5,11)) {
  res_P <- cor.test(diversity$value,diversity[,i],method = "pearson")
  res_S <- cor.test(diversity$value,diversity[,i],method = "spearman")
  cor_pval_P <- res_P$p.value
  cor_value_P <- res_P$estimate
  cor_pval_S <- res_S$p.value
  cor_value_S <- res_S$estimate
  cor.personal.table[j,1] <- cor_pval_P
  cor.personal.table[j,2] <- cor_value_P
  cor.personal.table[j,3] <- cor_pval_S
  cor.personal.table[j,4] <- cor_value_S
  j=j+1
}
j=1
for (i in 13:44) {
  res_P <- cor.test(diversity$value,diversity[,i],method = "pearson")
  res_S <- cor.test(diversity$value,diversity[,i],method = "spearman")
  cor_pval_P <- res_P$p.value
  cor_value_P <- res_P$estimate
  cor_pval_S <- res_S$p.value
  cor_value_S <- res_S$estimate
  cor.nutrient.table[j,1] <- cor_pval_P
  cor.nutrient.table[j,2] <- cor_value_P
  cor.nutrient.table[j,3] <- cor_pval_S
  cor.nutrient.table[j,4] <- cor_value_S
  j=j+1
}
j=1
for (i in 45:68) {
  res_P <- cor.test(diversity$value,diversity[,i],method = "pearson")
  res_S <- cor.test(diversity$value,diversity[,i],method = "spearman")
  cor_pval_P <- res_P$p.value
  cor_value_P <- res_P$estimate
  cor_pval_S <- res_S$p.value
  cor_value_S <- res_S$estimate
  cor.foods.table[j,1] <- cor_pval_P
  cor.foods.table[j,2] <- cor_value_P
  cor.foods.table[j,3] <- cor_pval_S
  cor.foods.table[j,4] <- cor_value_S
  j=j+1
}
rownames(cor.personal.table) <- c("Age","BMI")
rownames(cor.nutrient.table) <- colnames(diversity)[13:44]
rownames(cor.foods.table) <- colnames(diversity)[45:68]

write.csv(cor.personal.table,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/TAXA/cor_AlphaD_METADATA/cor_personal.csv")
write.csv(cor.nutrient.table,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/TAXA/cor_AlphaD_METADATA/cor_nutrient.csv")
write.csv(cor.foods.table,"/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/TAXA/cor_AlphaD_METADATA/cor_foods.csv")

cor.sig.spearman <- read.csv("/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/TAXA/cor_AlphaD_METADATA/cor_Spearman_significant.csv",header = T,row.names = 1,sep = "\t")

ggplot(cor.sig.spearman,aes(x=reorder(Metadata,cor_S),y=cor_S,fill=Type)) +
  geom_bar(aes(fill = Type), stat = "identity",
           show.legend = FALSE,
           color = "white") + # Border color
  xlab("Metadata") +
  ylab("Spearman correlation") +
  scale_y_continuous(breaks= seq(-1, 1, by = 0.1),
                     limits = c(min(cor.sig.spearman$cor_S),
                                max(cor.sig.spearman$cor_S))) +
  coord_flip() +
  theme_pubr()+ theme(text = element_text(size=20),legend.position = "none")+
  scale_fill_brewer(palette = "Dark2")

####### Maaslin2 #######
library(Maaslin2)
diversity_otu <- read.csv("E:/vhir/Enrichment/diversity_otu.csv",header = T,row.names = 1)
maaslin_otu <- data.frame(otu_table(subset_samples(phy_all_clean, disease != "UC")))
maaslin_metadata <- data.frame(sample_data(subset_samples(phy_all_clean, disease != "UC")))
maaslin_metadata$cd_localization[is.na(maaslin_metadata$cd_localization)] <- "None"

Maaslin2(
  diversity_otu,
  metadata_lm,
  output = "E:/vhir/Enrichment/STATISTICS/cor_AlphaD_METADATA/MAASLIN2/Personal",
  min_abundance = 0.0,
  min_prevalence = 0.0,
  min_variance = 0.0,
  normalization = "NONE",
  transform = "NONE",
  analysis_method = "LM",
  max_significance = 0.1,
  fixed_effects = c("BirthType","BMI","Age","Gender","BloodType"),
  correction = "BH",
  standardize = TRUE,
  cores = 1,
  plot_heatmap = TRUE,
  plot_scatter = TRUE,
  heatmap_first_n = 50,
  reference = NULL
)
# fixed_effects = c("N1","N2","N3","N4","N5","N6","N7","N8","N9","N10","N11","N12","N13","N14","N15","N16","N17","N18","N19","N20","N21","N22","N23","N24","N25","N26","N27","N28","N29","N30","N31","N32")
# fixed_effects = c("FGs13","FGs40","FGs47","FGs29","FGs35","FGs48","FGs12","FGs45","FGs18","FGs42","FGs17","FGs52","FGs37","FGs41","FGs24","FGs53")
# fixed_effects = c("BirthType","BMI","Age","Gender","BloodType")
```

Maaslin2_TAXA
```{r}
library(Maaslin2)
maaslin_otu <- data.frame(otu_table(subset_samples(myco_phy_all)))
maaslin_metadata <- data.frame(sample_data(subset_samples(myco_phy_all)))

for (i in 32:58) {
 fgs <- paste0("FGs",i)
 Maaslin2(
  maaslin_otu,
  maaslin_metadata,
  output = paste0("E:/vhir/Enrichment/STATISTICS/MAASLIN2/FoodGroups/",fgs),
  min_abundance = 0.0,
  min_prevalence = 0.0,
  min_variance = 0.0,
  normalization = "NONE",
  transform = "NONE",
  analysis_method = "LM",
  max_significance = 0.1,
  fixed_effects = c(fgs),
  correction = "BH",
  standardize = TRUE,
  cores = 1,
  plot_heatmap = TRUE,
  plot_scatter = TRUE,
  heatmap_first_n = 50,
  reference = NULL
)
}
Maaslin2(
  maaslin_otu,
  maaslin_metadata,
  output = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/TAXA/MAASLIN2/Partition",
  min_abundance = 0.0,
  min_prevalence = 0.0,
  min_variance = 0.0,
  normalization = "NONE",
  transform = "NONE",
  analysis_method = "LM",
  max_significance = 0.5,
  fixed_effects = c("Partition"),
  correction = "BH",
  standardize = TRUE,
  cores = 1,
  plot_heatmap = TRUE,
  plot_scatter = TRUE,
  heatmap_first_n = 50,
  reference = c("Partition","Control")
)

```

Maaslin2_FUNC
```{r}
library(Maaslin2)
maaslin_otu <- data.frame(otu_table(subset_samples(func_phy)))
maaslin_metadata <- data.frame(sample_data(subset_samples(func_phy)))

for (i in 32:58) {
 fgs <- paste0("FGs",i)
 Maaslin2(
  maaslin_otu,
  maaslin_metadata,
  output = paste0("E:/vhir/Enrichment/STATISTICS/MAASLIN2/FoodGroups/",fgs),
  min_abundance = 0.0,
  min_prevalence = 0.0,
  min_variance = 0.0,
  normalization = "NONE",
  transform = "NONE",
  analysis_method = "LM",
  max_significance = 0.1,
  fixed_effects = c(fgs),
  correction = "BH",
  standardize = TRUE,
  cores = 1,
  plot_heatmap = TRUE,
  plot_scatter = TRUE,
  heatmap_first_n = 50,
  reference = NULL
)
}
Maaslin2(
  maaslin_otu,
  maaslin_metadata,
  output = "/mnt/synology/ZIXUAN/LongitudinalMycobiome/STATISTICS/FUNC/MAASLIN/Partition",
  min_abundance = 0.0,
  min_prevalence = 0.0,
  min_variance = 0.0,
  normalization = "NONE",
  transform = "NONE",
  analysis_method = "LM",
  max_significance = 0.1,
  fixed_effects = c("Partition"),
  correction = "BH",
  standardize = TRUE,
  cores = 1,
  plot_heatmap = TRUE,
  plot_scatter = TRUE,
  heatmap_first_n = 50,
  reference = c("Partition","Control")
)

```

Calculate DA 
```{r}
sig.list <- read.csv("/home/zixuan/00-BACKUP/META/analysis/Maaslin/cd_uc_merge_sig_list.txt", sep = '\t',header = F)
da_table <- data.frame()
abundance_table <- data.frame()
for (i in sig.list$V1){
 df <- data.frame(Abundance = abundances(phyloseq_sub)[i,],
                  Group = meta(phyloseq_sub)$disease)
 # uc <- mean(df[df$Group=="UC",]$Abundance)
 uc <- mean(df[df$Group=="UC",]$Abundance)
 cd <- mean(df[df$Group=="CD",]$Abundance)
 da_table <- rbind(da_table,paste(i,cd-uc,sep = "|"))
 df <- aggregate(df[,1], list(df$Group), mean)
 df['pwy']=i
 abundance_table <- rbind(abundance_table,df)
}
colnames(da_table) <- "taxa|cd-uc"
colnames(abundance_table) <- c("Group","Abundance","taxa")
# write.csv(abundance_table,"E:/vhir/DB/meta/functional/analysis/Maaslin/china/ESRD/abundance_table.csv",row.names = T)
write.csv(da_table,"/home/zixuan/00-BACKUP/META/analysis/Maaslin/cd_uc_da_path.csv",row.names = FALSE)
write.csv(abundance_table,"/home/zixuan/00-BACKUP/META/analysis/Maaslin/cd_uc_abundance.csv",row.names = FALSE)
```

Plot DA
```{r}


```


