---
title: "mock_pop_genus"
author: "Aleix Canalda"
date: "3/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


MOCK POPULATION FUNCTIONS
```{r}
create_taxa_table <- function(taxonomy_df,n_col){
  for (i in 1:nrow(taxonomy_df)) {
    taxa=taxonomy_df[i,n_col]
    tax_list=strsplit(taxa,";")
    kingdom=tax_list[[1]][1]
    phylum=tax_list[[1]][2]
    class=tax_list[[1]][3]
    order=tax_list[[1]][4]
    family=tax_list[[1]][5]
    genus=tax_list[[1]][6]
    specie=tax_list[[1]][7]
    strain=tax_list[[1]][8]

    if (!exists("taxa_table")){
      taxa_table<- data.frame(kingdom, phylum, class, order, family, genus, specie,strain)
      } 
    else if (exists("taxa_table")){
      taxa_table <- rbind(taxa_table, c(kingdom, phylum, class, order, family, genus, specie,strain))
    }
  }
  taxa_table[is.na(taxa_table)] <- "No"
  colnames(taxa_table) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "genus","Strain")
  return(taxa_table)
}
mockits <- function(pop){
  mg_depth <- read.table(paste("/mnt/synology/ALEIX/mock_pop/mockits_",pop,".depth.30.txt.gz",sep=""), header = FALSE, sep = "\t")
  genes <-unique(mg_depth[,1])

  trimmed_mg_depth <- mg_depth %>%
    group_by(V1) %>%
    filter(.,  V2 > 50  & V2 < max(V2)-50) %>%
    filter(., V3 > 15)
  trimmed_mg_mean <- trimmed_mg_depth %>%
    group_by(V1) %>%
    summarise(Mean = mean(V3, na.rm = TRUE),Length = max(V2))
  print(trimmed_mg_mean)
  write.table(trimmed_mg_mean[,1],paste("/mnt/synology/ALEIX/mock_pop/transition/mockits_",pop,".txt",sep=""),row.names = FALSE)
  return(trimmed_mg_mean)
}
mockits2 <- function(pop,trimmed_mg_mean){
  tax <- read.table(paste("/mnt/synology/ALEIX/mock_pop/transition/mockits_",pop,"_tax2.txt",sep=""))
  trimmed_mg_mean <- merge(trimmed_mg_mean,tax)
  taxa2_table <- create_taxa_table(taxonomy_df = trimmed_mg_mean,n_col = 4)
  trimmed_mg_mean <- cbind(trimmed_mg_mean,taxa2_table)
#get rel ab of each taxa
#trimmed_mg_mean[trimmed_mg_mean$genus=="s__unidentified" & trimmed_mg_mean$Genus=="g__Aspergillus",]$genus <- "s__Aspergillus_flavus"
#trimmed_mg_mean[trimmed_mg_mean$genus=="s__unidentified" & trimmed_mg_mean$Genus=="g__Saccharomyces",]$genus <- "s__Saccharomyces_cerevisiae"
#trimmed_mg_mean[trimmed_mg_mean$genus=="s__unidentified" & trimmed_mg_mean$Genus=="g__Candida",]$genus <- "s__Candida_albicans"
  mock_relab <- trimmed_mg_mean %>%
  #filter(.,Mean > 4) %>%
    mutate(.,rel_ab = Mean/sum(Mean)) %>%
    group_by(Genus) %>%
    summarise(.,genus_rel_ab = sum(rel_ab))
  mock_relab$Method <- "ITS"
  return(mock_relab)
}
mockshot <- function(pop){
  shot_depth <- read.table(paste("/mnt/synology/ALEIX/mock_pop/mock_",pop,".depth.30.txt.gz",sep=""), header = FALSE, sep = "\t")
  genes <-unique(shot_depth[,1])

  shot_mg_depth <- shot_depth %>%
    group_by(V1) %>%
    filter(.,  V2 > 50  & V2 < max(V2)-50) %>%
    filter(., V3 > 15)

  shot_mg_mean <- shot_mg_depth %>%
    summarise(Length = max(V2),genus = strsplit(V1,"|",fixed=TRUE)[[1]][1],Depth=V3) %>%
    group_by(genus) %>%
    summarise(Mean = mean(Depth, na.rm = TRUE)) %>%
  #filter(.,Mean > 4) %>%
    summarise(genus = genus, rel_ab = Mean/sum(Mean),Mean=Mean)
  id_to_tax <- read_excel("/home/aleix/Documents/MASTER/ITS/busco_all_taxonomy4331.xlsx")
  shot_mg_mean <- merge(shot_mg_mean,id_to_tax, by.x = 1,by.y=1)
  shot_mg_relab <- shot_mg_mean %>%
    group_by(Genus) %>%
    summarise(.,genus_rel_ab=sum(rel_ab))
  shot_mg_relab$Method <- "Shotgun"
  return(shot_mg_relab)
}
```

```{r}
mg_depth <- read.table("/mnt/synology/ALEIX/mock_pop/mockits.depth_30.c80.txt.gz", header = FALSE, sep = "\t")
genes <-unique(mg_depth[,1])

trimmed_mg_depth <- mg_depth %>%
  group_by(V1) %>%
  filter(.,  V2 > 50  & V2 < max(V2)-50) %>%
  filter(., V3 > 15)
trimmed_mg_mean <- trimmed_mg_depth %>%
  group_by(V1) %>%
  summarise(Mean = mean(V3, na.rm = TRUE),Length = max(V2))
write.table(trimmed_mg_mean[,1],"/mnt/synology/ALEIX/mock_pop/transition/mockits.txt",row.names = FALSE) # eliminate " with sed and " " with _
```
bash commands to modify and obtain full taxonomy
```{r}
tax <- read.table("/mnt/synology/ALEIX/mock_pop/transition/mockits_tax2.txt")
trimmed_mg_mean <- merge(trimmed_mg_mean,tax)
taxa2_table <- create_taxa_table(taxonomy_df = trimmed_mg_mean,n_col = 4)
trimmed_mg_mean <- cbind(trimmed_mg_mean,taxa2_table)
#get rel ab of each taxa
#trimmed_mg_mean[trimmed_mg_mean$genus=="s__unidentified" & trimmed_mg_mean$Genus=="g__Aspergillus",]$genus <- "s__Aspergillus_flavus"
#trimmed_mg_mean[trimmed_mg_mean$genus=="s__unidentified" & trimmed_mg_mean$Genus=="g__Saccharomyces",]$genus <- "s__Saccharomyces_cerevisiae"
#trimmed_mg_mean[trimmed_mg_mean$genus=="s__unidentified" & trimmed_mg_mean$Genus=="g__Candida",]$genus <- "s__Candida_albicans"
mock_relab <- trimmed_mg_mean %>%
  #filter(.,Mean > 4) %>%
  mutate(.,rel_ab = Mean/sum(Mean)) %>%
  group_by(Genus) %>%
  summarise(.,genus_rel_ab = sum(rel_ab))
mock_relab$Method <- "ITS"
```

MOCK POPULATION - Shotgun
```{r}
shot_depth <- read.table("/mnt/synology/ALEIX/mock_pop/mock.depth_30.c80.txt.gz", header = FALSE, sep = "\t")
genes <-unique(shot_depth[,1])

shot_mg_depth <- shot_depth %>%
  group_by(V1) %>%
  filter(.,  V2 > 50  & V2 < max(V2)-50) %>%
  filter(., V3 > 15)

shot_mg_mean <- shot_mg_depth %>%
  summarise(Length = max(V2),genus = strsplit(V1,"|",fixed=TRUE)[[1]][1],Depth=V3) %>%
  group_by(genus) %>%
  summarise(Mean = mean(Depth, na.rm = TRUE)) %>%
  #filter(.,Mean > 4) %>%
  summarise(genus = genus, rel_ab = Mean/sum(Mean), Mean=Mean)
id_to_tax <- read_excel("/home/aleix/Documents/MASTER/ITS/busco_all_taxonomy4331.xlsx")
shot_mg_mean <- merge(shot_mg_mean,id_to_tax, by.x = 1,by.y=1)
shot_mg_relab <- shot_mg_mean %>%
  group_by(Genus) %>%
  summarise(.,genus_rel_ab=sum(rel_ab))
shot_mg_relab$Method <- "Shotgun"
```

COMPARISON POP 1
```{r}

comparison <- rbind(shot_mg_relab,mock_relab)
comparison <- comparison %>%
  mutate(Genus=str_remove(Genus,"g__")) %>%
  mutate(Genus=str_replace(Genus,"__"," ")) %>%
  mutate(Genus=str_replace(Genus,"_"," ")) %>%
  arrange(desc(genus_rel_ab)) %>%
  mutate(Genus = case_when(
            Genus =="Candida" ~ "Candida",
            Genus =="Saccharomyces" ~ "Saccharomyces",
            Genus =="Rhodotorula" ~ "Rhodotorula",
            Genus =="Aspergillus" ~ "Aspergillus",
            TRUE ~ "Other"))
write.table(comparison,"/mnt/synology/ALEIX/comparison.tbl",sep="\t",row.names = FALSE)

#comparison$genus <- factor(comparison$genus,levels = comparison$genus)
mynames <- unique(comparison$Genus)
mycolours <- scales::hue_pal()(length(mynames))
mycolours <- setNames(mycolours, mynames)
# set up custom colour!
mycolours[c("Candida","Saccharomyces","Aspergillus","Rhodotorula")] <- c("greenyellow","yellow3","turquoise","sienna")
myalphas <- rep(0.2, length(mynames))
myalphas <- setNames(myalphas, mynames)
myalphas[c("Candida albicans","Saccharomyces cerevisiae","Aspergillus flavus","Rhodotorula mucilaginosa")] <- 1

comparison2 <- comparison %>%
  group_by(Genus,Method) %>%
  summarise(total_rel_ab = sum(genus_rel_ab))

ggplot(comparison2,aes(x=Method,y=total_rel_ab, fill=Genus, group=total_rel_ab, label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5))

expected <- data.frame(genus=c("Candida","Candida","Aspergillus","Aspergillus","Rhodotorula","Rhodotorula","Saccharomyces","Saccharomyces"),Method=c("ITS","Shotgun","ITS","Shotgun","ITS","Shotgun","ITS","Shotgun"),total_rel_ab=c(0.177,0.35,0.469,0.35,0.118,0.15,0.236,0.15))

ggplot(expected,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab, label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black", width = 0.3) +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5)) +
  theme(aspect.ratio = 1.5/1)
```

POPULATION 2
```{r}
mgmean2 <- mockits("pop2")
relab_its_pop2 <- mockits2("pop2",mgmean2)
relab_shot_pop2 <- mockshot("pop2.2")
```
COMPARISON POP 2
```{r}

comparison_pop2 <- rbind(relab_shot_pop2,relab_its_pop2)
comparison_pop2 <- comparison_pop2 %>%
  mutate(Genus=str_remove(Genus,"g__")) %>%
  mutate(Genus=str_replace(Genus,"__"," ")) %>%
  mutate(Genus=str_replace(Genus,"_"," ")) %>%
  arrange(desc(genus_rel_ab)) %>%
  mutate(Genus = case_when(
            Genus =="Candida" ~ "Candida",
            Genus =="Rhizopus" ~ "Rhizopus",
            TRUE ~ "Other"))
#comparison$genus <- factor(comparison$genus,levels = comparison$genus)
mynames_pop2 <- unique(comparison_pop2$Genus)
mycolours_pop2 <- scales::hue_pal()(length(mynames_pop2))
mycolours_pop2 <- setNames(mycolours_pop2, mynames_pop2)
# set up custom colour!
mycolours[c("Candida","Rhizopus")] <- c("greenyellow","aquamarine")
myalphas <- rep(0.2, length(mynames))
myalphas <- setNames(myalphas, mynames)
myalphas[c("Candida albicans","Saccharomyces cerevisiae","Aspergillus flavus","Rhodotorula mucilaginosa")] <- 1

comparison2_pop2 <- comparison_pop2 %>%
  group_by(Genus,Method) %>%
  summarise(total_rel_ab = sum(genus_rel_ab))

ggplot(comparison2_pop2,aes(x=Method,y=total_rel_ab, fill=Genus, group=total_rel_ab, label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5))

expected_pop2 <- data.frame(genus=c("Candida","Candida","Rhizopus", "Rhizopus"), Method=c("ITS","Shotgun","ITS","Shotgun"),total_rel_ab=c(0.574,0.729,0.426,0.271))

ggplot(expected_pop2,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab, label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black", width = 0.3) +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5)) +
  theme(aspect.ratio = 1.5/1)
```

POPULATION 3
```{r}
mgmean3 <- mockits("pop3")
relab_its_pop3 <- mockits2("pop3",mgmean3)
relab_shot_pop3 <- mockshot("pop3")
```

COMPARISON POP 3
```{r}
colnames(relab_shot_pop3) <- c("genus","genus_rel_ab","Method")
colnames(relab_its_pop3) <- c("genus","genus_rel_ab","Method")
comparison_pop3 <- rbind(relab_its_pop3,relab_shot_pop3)
comparison_pop3 <- comparison_pop3 %>%
  mutate(genus=str_remove(genus,"g__")) %>%
  mutate(genus=str_replace(genus,"__"," ")) %>%
  mutate(genus=str_replace(genus,"_"," ")) %>%
  arrange(desc(genus_rel_ab)) %>%
  mutate(genus2 = case_when(
            genus =="Saccharomyces" ~ "Saccharomyces",
            genus =="Aspergillus" ~ "Aspergillus",
            genus =="Cryptococcus" ~ "Cryptococcus",
            TRUE ~ "Other"))
write.table(comparison_pop3,"/mnt/synology/ALEIX/comparison_pop3.tbl",sep="\t",row.names = FALSE)

#comparison$genus <- factor(comparison$genus,levels = comparison$genus)
mynames <- unique(comparison_pop3$genus2)
mycolours <- scales::hue_pal()(length(mynames))
mycolours <- setNames(mycolours, mynames)
# set up custom colour!
mycolours[c("Saccharomyces","Aspergillus","Cryptococcus")] <- c("yellow3","turquoise","darkcyan")
myalphas <- rep(0.2, length(mynames))
myalphas <- setNames(myalphas, mynames)
myalphas[c("Saccharomyces cerevisiae","Aspergillus flavus","Cryptococcus neoformans")] <- 1

comparison2_pop3 <- comparison_pop3 %>%
  group_by(genus2,Method) %>%
  summarise(total_rel_ab = sum(genus_rel_ab))

ggplot(comparison2_pop3,aes(x=Method,y=total_rel_ab, fill=genus2, group=total_rel_ab,label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5)) +
  theme(legend.position = "right")

expected_pop3 <- data.frame(genus=c("Aspergillus","Aspergillus","Saccharomyces","Saccharomyces","Cryptococcus", "Cryptococcus"),Method=c("ITS","Shotgun","ITS","Shotgun","ITS","Shotgun"),total_rel_ab=c(0.555,0.48,0.295,0.28,0.15,0.24))

ggplot(expected_pop3,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab,label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black", width = 0.3) +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5)) +
  theme(aspect.ratio = 1.5/1)
```

POPULATION 4
```{r}
mgmean4 <- mockits("pop4")
relab_its_pop4 <- mockits2("pop4",mgmean4)
relab_shot_pop4 <- mockshot("pop4")
```

COMPARISON POP 4
```{r}
colnames(relab_shot_pop4) <- c("genus","genus_rel_ab","Method")
colnames(relab_its_pop4) <- c("genus","genus_rel_ab","Method")
comparison_pop4 <- rbind(relab_its_pop4,relab_shot_pop4)
comparison_pop4 <- comparison_pop4 %>%
  mutate(genus=str_remove(genus,"g__")) %>%
  mutate(genus=str_replace(genus,"__"," ")) %>%
  mutate(genus=str_replace(genus,"_"," ")) %>%
  arrange(desc(genus_rel_ab)) %>%
  mutate(genus2 = case_when(
            genus =="Rhodotorula" ~ "Rhodotorula",
            genus =="Rhizopus" ~ "Rhizopus",
            TRUE ~ "Other"))
#write.table(comparison_pop2,"/mnt/synology/ALEIX/comparison_pop2.tbl",sep="\t",row.names = FALSE)

#comparison$genus <- factor(comparison$genus,levels = comparison$genus)
mynames <- unique(comparison_pop4$genus2)
mycolours <- scales::hue_pal()(length(mynames))
mycolours <- setNames(mycolours, mynames)
# set up custom colour!
mycolours[c("Rhodotorula","Rhizopus")] <- c("sienna","aquamarine")
myalphas <- rep(0.2, length(mynames))
myalphas <- setNames(myalphas, mynames)
myalphas[c("Rhodotorula mucilaginosa","Rhizopus oryzae")] <- 1

comparison2_pop4 <- comparison_pop4 %>%
  group_by(genus2,Method) %>%
  summarise(total_rel_ab = sum(genus_rel_ab))

ggplot(comparison2_pop4,aes(x=Method,y=total_rel_ab, fill=genus2, group=total_rel_ab,label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5))

expected_pop4 <- data.frame(genus=c("Rhodotorula","Rhodotorula","Rhizopus", "Rhizopus"), Method=c("ITS","Shotgun","ITS","Shotgun"),total_rel_ab=c(0.5397,0.3334,0.4603,0.6666))

ggplot(expected_pop4,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab, label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black", width = 0.3) +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5)) +
  theme(aspect.ratio = 1.5/1)
```

POPULATION 5
```{r}
mgmean5 <- mockits("pop5")
relab_its_pop5 <- mockits2("pop5",mgmean5)
relab_shot_pop5 <- mockshot("pop5")
```

COMPARISON POP 5
```{r}
colnames(relab_shot_pop5) <- c("genus","genus_rel_ab","Method")
colnames(relab_its_pop5) <- c("genus","genus_rel_ab","Method")
comparison_pop5 <- rbind(relab_its_pop5,relab_shot_pop5)
comparison_pop5 <- comparison_pop5 %>%
  mutate(genus=str_remove(genus,"g__")) %>%
  mutate(genus=str_replace(genus,"__"," ")) %>%
  mutate(genus=str_replace(genus,"_"," ")) %>%
  arrange(desc(genus_rel_ab)) %>%
  mutate(genus2 = case_when(
            genus =="Candida" ~ "Candida",
            TRUE ~ "Other"))
#write.table(comparison_pop2,"/mnt/synology/ALEIX/comparison_pop2.tbl",sep="\t",row.names = FALSE)

#comparison$genus <- factor(comparison$genus,levels = comparison$genus)
mynames <- unique(comparison_pop5$genus2)
mycolours <- scales::hue_pal()(length(mynames))
mycolours <- setNames(mycolours, mynames)
# set up custom colour!
mycolours[c("Candida","Other")] <- c("greenyellow","gray")
myalphas <- rep(0.2, length(mynames))
myalphas <- setNames(myalphas, mynames)
myalphas[c("Candida albicans")] <- 1

comparison2_pop5 <- comparison_pop5 %>%
  group_by(genus2,Method) %>%
  summarise(total_rel_ab = sum(genus_rel_ab))

ggplot(comparison2_pop5,aes(x=Method,y=total_rel_ab, fill=genus2, group=total_rel_ab,label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5))

expected_pop5 <- data.frame(genus=c("Candida","Candida"), Method=c("ITS","Shotgun"),total_rel_ab=c(1,1))

ggplot(expected_pop5,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab,label=total_rel_ab)) +
  geom_bar(stat = "identity",color="black", width = 0.3) +
  theme_pubr() +
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  geom_label(position = position_stack(vjust = 0.5)) +
  theme(aspect.ratio = 1.5/1)
```

Join obs and exp into one dataframe, for each pop
```{r}
colnames(comparison2) <- c("genus","Method","total_rel_ab")
comparison2_pca <- comparison2[] %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(comparison2_pca) <- c("ITS_pop1","Shotgun_pop1")
expected_pca <- expected %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(expected_pca) <- c("ITS_exp","Shotgun_exp")
full_pop1 <- merge(expected_pca,comparison2_pca,by=0,all=T) %>%
  column_to_rownames(.,var="Row.names")
full_pop1[is.na(full_pop1)] <- 0

colnames(comparison2_pop2) <- c("genus","Method","total_rel_ab")
comparison2_pca_pop2 <- comparison2_pop2[] %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   rbind(.,data_frame(genus="Rhizopus","ITS"=0,"Shotgun"=NA)) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(comparison2_pca_pop2) <- c("ITS_pop1","Shotgun_pop1")
expected_pca_pop2 <- expected_pop2 %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(expected_pca_pop2) <- c("ITS_exp","Shotgun_exp")
full_pop2 <- merge(expected_pca_pop2,comparison2_pca_pop2,by=0,all=T) %>%
  column_to_rownames(.,var="Row.names")
full_pop2[is.na(full_pop2)] <- 0

colnames(comparison2_pop3) <- c("genus","Method","total_rel_ab")
comparison2_pca_pop3 <- comparison2_pop3[] %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(comparison2_pca_pop3) <- c("ITS_pop1","Shotgun_pop1")
expected_pca_pop3 <- expected_pop3 %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(expected_pca_pop3) <- c("ITS_exp","Shotgun_exp")
full_pop3 <- merge(expected_pca_pop3,comparison2_pca_pop3,by=0,all=T) %>%
  column_to_rownames(.,var="Row.names")
full_pop3[is.na(full_pop3)] <- 0

colnames(comparison2_pop4) <- c("genus","Method","total_rel_ab")
comparison2_pca_pop4 <- comparison2_pop4[] %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   rbind(.,data_frame(genus="Rhizopus","ITS"=0,"Shotgun"=NA)) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(comparison2_pca_pop4) <- c("ITS_pop1","Shotgun_pop1")
expected_pca_pop4 <- expected_pop4 %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(expected_pca_pop4) <- c("ITS_exp","Shotgun_exp")
full_pop4 <- merge(expected_pca_pop4,comparison2_pca_pop4,by=0,all=T) %>%
  column_to_rownames(.,var="Row.names")
full_pop4[is.na(full_pop4)] <- 0

colnames(comparison2_pop5) <- c("genus","Method","total_rel_ab")
comparison2_pca_pop5 <- comparison2_pop5[] %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(comparison2_pca_pop5) <- c("ITS_pop1","Shotgun_pop1")
expected_pca_pop5 <- expected_pop5 %>% 
   mutate(rn = row_number()) %>%
   spread(Method, total_rel_ab) %>%
   dplyr::select(-rn) %>%
   group_by(genus) %>%
   summarise_all(na.omit) %>%
   column_to_rownames(.,var="genus")
colnames(expected_pca_pop5) <- c("ITS_exp","Shotgun_exp")
full_pop5 <- merge(expected_pca_pop5,comparison2_pca_pop5,by=0,all=T) %>%
  column_to_rownames(.,var="Row.names")
full_pop5[is.na(full_pop5)] <- 0

full <- rbind(full_pop1,full_pop2)
full <- rbind(full,full_pop3)
full <- rbind(full,full_pop4)
full <- rbind(full, full_pop5)
#pca_data <- data.frame(model$x,pop = colnames(full))
#ggplot(pca_data, aes(x=PC1, y=PC2, color = pop)) + geom_point() + theme_pubr()
mock_meta <- data.frame(Type=c("Expected","Expected","Observed","Observed"),Method=c("ITS","Shotgun","ITS","Shotgun"),row.names = colnames(full))
```

Calculating wUnifrac distances of each population and t test:

```{r taxa matrix}
set.seed(10)
#ALL POPULATIONS TOGETHER
otable <- otu_table(full,taxa_are_rows = T)
mdata <- sample_data(mock_meta)

phy_genus <- phyloseq(otable, mdata)

random_tree = rtree(ntaxa(phy_genus), rooted=TRUE, tip.label=taxa_names(phy_genus))
phy_genus <- phyloseq(otable, mdata, random_tree)
wunifrac_dist = phyloseq::distance(phy_genus, method="unifrac", weighted=T)
ordination = ordinate(phy_genus, method="PCoA", distance=wunifrac_dist)
adonis_res <- adonis2(wunifrac_dist~sample_data(phy_genus)$Type)


p <- plot_ordination(phy_genus, ordination, color="Method") +
 theme(aspect.ratio=1)+ theme_pubr()
#  scale_color_manual(values = col_vector) +
 # scale_fill_manual(values = col_vector) +
  #ggtitle("Pathways clustering (weighted unifrac)") +
  #theme(plot.title = element_text(hjust = 0.5),text = element_text(size=30)) +
   # theme_pubr()
  #stat_ellipse(aes(fill = disease), geom="polygon",level=0.95,alpha=0.2)
  
#POPULATION 2
  
otable_pop2 <- otu_table(full_pop2,taxa_are_rows = T)
mdata <- sample_data(mock_meta)
phy_genus_pop2 <- phyloseq(otable_pop2, mdata)
random_tree_pop2 = rtree(ntaxa(phy_genus_pop2), rooted=TRUE, tip.label=taxa_names(phy_genus_pop2))
phy_genus_pop2 <- phyloseq(otable_pop2, mdata, random_tree_pop2)
wunifrac_dist_pop2 = phyloseq::distance(phy_genus_pop2, method="unifrac", weighted=T)
ordination_pop2 = ordinate(phy_genus_pop2, method="PCoA", distance=wunifrac_dist_pop2)
adonis_res_pop2 <- adonis2(wunifrac_dist_pop2~sample_data(phy_genus_pop2)$Type)
p <- plot_ordination(phy_genus_pop2, ordination, color="Method") +
 theme(aspect.ratio=1)+ theme_pubr()
  
#POPULATION 1
otable_pop1 <- otu_table(full_pop1,taxa_are_rows = T)
mdata <- sample_data(mock_meta)
phy_genus_pop1 <- phyloseq(otable_pop1, mdata)
random_tree_pop1 = rtree(ntaxa(phy_genus_pop1), rooted=TRUE, tip.label=taxa_names(phy_genus_pop1))
phy_genus_pop1 <- phyloseq(otable_pop1, mdata, random_tree_pop1)
wunifrac_dist_pop1 = phyloseq::distance(phy_genus_pop1, method="unifrac", weighted=T)
ordination_pop1 = ordinate(phy_genus_pop1, method="PCoA", distance=wunifrac_dist_pop1)
adonis_res_pop1 <- adonis2(wunifrac_dist_pop1~sample_data(phy_genus_pop1)$Type)
p_pop1 <- plot_ordination(phy_genus_pop1, ordination, color="Method") +
 theme(aspect.ratio=1)+ theme_pubr()

#POPULATION 3
otable_pop3 <- otu_table(full_pop3,taxa_are_rows = T)
mdata <- sample_data(mock_meta)
phy_genus_pop3 <- phyloseq(otable_pop3, mdata)
random_tree_pop3 = rtree(ntaxa(phy_genus_pop3), rooted=TRUE, tip.label=taxa_names(phy_genus_pop3))
phy_genus_pop3 <- phyloseq(otable_pop3, mdata, random_tree_pop3)
wunifrac_dist_pop3 = phyloseq::distance(phy_genus_pop3, method="unifrac", weighted=T)
ordination_pop3 = ordinate(phy_genus_pop3, method="PCoA", distance=wunifrac_dist_pop3)
adonis_res_pop3 <- adonis2(wunifrac_dist_pop3~sample_data(phy_genus_pop3)$Type)
p <- plot_ordination(phy_genus, ordination, color="Method") +
 theme(aspect.ratio=1)+ theme_pubr()

#POPULATION 4
otable_pop4 <- otu_table(full_pop4,taxa_are_rows = T)
mdata <- sample_data(mock_meta)
phy_genus_pop4 <- phyloseq(otable_pop4, mdata)
random_tree_pop4 = rtree(ntaxa(phy_genus_pop4), rooted=TRUE, tip.label=taxa_names(phy_genus_pop4))
phy_genus_pop4 <- phyloseq(otable_pop4, mdata, random_tree_pop4)
wunifrac_dist_pop4 = phyloseq::distance(phy_genus_pop4, method="unifrac", weighted=T)
ordination_pop4 = ordinate(phy_genus_pop4, method="PCoA", distance=wunifrac_dist_pop4)
adonis_res_pop4 <- adonis2(wunifrac_dist_pop4~sample_data(phy_genus_pop4)$Type)
p <- plot_ordination(phy_genus, ordination, color="Method") +
 theme(aspect.ratio=1)+ theme_pubr()

#POPULATION 5
otable_pop5 <- otu_table(full_pop5,taxa_are_rows = T)
mdata <- sample_data(mock_meta)
phy_genus_pop5 <- phyloseq(otable_pop5, mdata)
random_tree_pop5 = rtree(ntaxa(phy_genus_pop5), rooted=TRUE, tip.label=taxa_names(phy_genus_pop5))
phy_genus_pop5 <- phyloseq(otable_pop5, mdata, random_tree_pop5)
wunifrac_dist_pop5 = phyloseq::distance(phy_genus_pop5, method="unifrac", weighted=T)
ordination_pop5 = ordinate(phy_genus_pop5, method="PCoA", distance=wunifrac_dist_pop5)
adonis_res_pop5 <- adonis2(wunifrac_dist_pop5~sample_data(phy_genus_pop5)$Type)
p <- plot_ordination(phy_genus, ordination, color="Method") +
 theme(aspect.ratio=1)+ theme_pubr()


#t Test
testing_itsexp <- data.frame(ITS=c(wunifrac_dist_pop1[2],wunifrac_dist_pop2[2],wunifrac_dist_pop3[2],wunifrac_dist_pop4[2],wunifrac_dist_pop5[2],wunifrac_dist_gut[2]),Shotgun=c(wunifrac_dist_pop1[5],wunifrac_dist_pop2[5],wunifrac_dist_pop3[5],wunifrac_dist_pop4[5],wunifrac_dist_pop5[5],wunifrac_dist_gut[5]))
t.test(testing_itsexp$ITS,testing_itsexp$Shotgun)
testing_itsshotgun <- data.frame(ITS=c(wunifrac_dist_pop1[4],wunifrac_dist_pop2[4],wunifrac_dist_pop3[4],wunifrac_dist_pop4[4],wunifrac_dist_pop5[4],wunifrac_dist_gut[4]),Shotgun=c(wunifrac_dist_pop1[5],wunifrac_dist_pop2[5],wunifrac_dist_pop3[5],wunifrac_dist_pop4[5],wunifrac_dist_pop5[5],wunifrac_dist_gut[5]))
t.test(testing_itsshotgun$ITS,testing_itsshotgun$Shotgun)
```
BEAUTIFUL PLOT
```{r}
mynames <- unique(c(comparison2_pop5$genus,comparison2_pop4$genus,comparison2_pop3$genus,comparison2_pop2$genus,comparison2$genus,comparison2_gut$genus))
mycolours <- scales::hue_pal()(length(mynames))
mycolours <- setNames(mycolours, mynames)
# set up custom colour!
mycolours[c("Saccharomyces","Dacryopinax","Aspergillus","Schizophyllum","Trichosporon","Candida","Geotrichum","Blastomyces","Debaryomyces","Yarrowia","Rhizopogon","Malassezia","Other","Rhodotorula","Rhizopus","Cryptococcus")] <- c("#a1def0", "#2f8fa5", "#c53607", "#ccabf0", "#8567bb","#d8dc35", "#21f0b6", "#166d2a", "#aee39a", "#4dc31e", "#673d17", "#f9905b","darkgray","#dbc58e","#a17f33","#0b29d0")

#mycolours[c("Candida","Other","Saccharomyces","Aspergillus","Rhodotorula","Rhizopus","Cryptococcus","Schizophyllum","Trichosporon","Candida","Geotrichum","Blastomyces","Debaryomyces","Yarrowia","Rhizopogon","Malassezia","Dacryopinax")] <- c("greenyellow","gray","yellow3","turquoise","sienna","steelblue1","darkcyan","honeydew3","lemonchiffon2","greenyellow","tan","snow2","navajowhite","lightgoldenrod","lightblue","ivory2","darkslategray")

#POP 5
comparison2_pop5 <- comparison2_pop5 %>% mutate(Method = case_when(
    Method == "ITS" ~ "ITS observed",
    Method == "Shotgun" ~ "Shotgun observed"
  ))
colnames(comparison2_pop5) <- c("genus","Method","total_rel_ab")
expected_pop5 <- expected_pop5 %>%mutate(Method = case_when(
    Method == "ITS" ~ "ITS expected",
    Method == "Shotgun" ~ "Shotgun expected"
  ))
expobs_pop5 <- rbind(comparison2_pop5,expected_pop5)
ggplot(expobs_pop5,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  #scale_alpha_manual(values=myalphas)+
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  theme(aspect.ratio = 0.5/2) +
  coord_flip()
  #geom_label(position = position_stack(vjust = 0.5))
expobs_pop5$Pop <- "Population 5"

#POP 4
comparison2_pop4 <- comparison2_pop4 %>% mutate(Method = case_when(
    Method == "ITS" ~ "ITS observed",
    Method == "Shotgun" ~ "Shotgun observed"
  ))
colnames(comparison2_pop4) <- c("genus","Method","total_rel_ab")
expected_pop4 <- expected_pop4 %>% mutate(Method = case_when(
    Method == "ITS" ~ "ITS expected",
    Method == "Shotgun" ~ "Shotgun expected"
  ))
expobs_pop4 <- rbind(comparison2_pop4,expected_pop4)
ggplot(expobs_pop4,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  #scale_alpha_manual(values=myalphas)+
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  theme(aspect.ratio = 0.5/2) +
  coord_flip()
  #geom_label(position = position_stack(vjust = 0.5))
expobs_pop4$Pop <- "Population 4"

#POP 3
comparison2_pop3 <- comparison2_pop3 %>% mutate(Method = case_when(
    Method == "ITS" ~ "ITS observed",
    Method == "Shotgun" ~ "Shotgun observed"
  ))
colnames(comparison2_pop3) <- c("genus","Method","total_rel_ab")
expected_pop3 <- expected_pop3 %>%mutate(Method = case_when(
    Method == "ITS" ~ "ITS expected",
    Method == "Shotgun" ~ "Shotgun expected"
  ))
expobs_pop3 <- rbind(comparison2_pop3,expected_pop3)
ggplot(expobs_pop3,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  #scale_alpha_manual(values=myalphas)+
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  theme(aspect.ratio = 0.5/2) +
  coord_flip()
  #geom_label(position = position_stack(vjust = 0.5))
expobs_pop3$Pop <- "Population 3"


#POP 2
comparison2_pop2 <- comparison2_pop2 %>% mutate(Method = case_when(
    Method == "ITS" ~ "ITS observed",
    Method == "Shotgun" ~ "Shotgun observed"
  ))
colnames(comparison2_pop2) <- c("genus","Method","total_rel_ab")
expected_pop2 <- expected_pop2 %>%mutate(Method = case_when(
    Method == "ITS" ~ "ITS expected",
    Method == "Shotgun" ~ "Shotgun expected"
  ))
expobs_pop2 <- rbind(comparison2_pop2,expected_pop2)
ggplot(expobs_pop2,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  #scale_alpha_manual(values=myalphas)+
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  theme(aspect.ratio = 0.5/2) +
  coord_flip()
  #geom_label(position = position_stack(vjust = 0.5))
expobs_pop2$Pop <- "Population 2"


#POP 1
comparison2 <- comparison2 %>% mutate(Method = case_when(
    Method == "ITS" ~ "ITS observed",
    Method == "Shotgun" ~ "Shotgun observed"
  ))
colnames(comparison2) <- c("genus","Method","total_rel_ab")
expected <- expected %>%mutate(Method = case_when(
    Method == "ITS" ~ "ITS expected",
    Method == "Shotgun" ~ "Shotgun expected"
  ))
expobs <- rbind(comparison2,expected)
ggplot(expobs,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  #scale_alpha_manual(values=myalphas)+
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  theme(aspect.ratio = 0.5/2) +
  coord_flip()
  #geom_label(position = position_stack(vjust = 0.5))
expobs$Pop <- "Population 1"
fullplot <- rbind(expobs,expobs_pop2)
fullplot <- rbind(fullplot,expobs_pop3)
fullplot <- rbind(fullplot,expobs_pop4)
fullplot <- rbind(fullplot,expobs_pop5)
fullplot <- rbind(fullplot,expobs_gut)
```

FINAL PLOT

```{r}
par(mar=c(3,3,3,0))
plot <- ggplot(fullplot,aes(x=Method,y=total_rel_ab, fill=genus, group=total_rel_ab)) +
  geom_bar(stat = "identity",color="black") +
  theme_pubr() +
  #scale_alpha_manual(values=myalphas)+
  labs(x = "Mock Community Identification Method",y = "genus Relative Abundance") +
  scale_fill_manual(values = mycolours) +
  theme(aspect.ratio = 0.5/2) +#,legend.position = c(0.65,0.15),legend.key.size = unit(0.6, "cm"),legend.direction = "horizontal") +
  coord_flip() +
  facet_wrap(. ~ Pop, ncol = 2) +
  labs(x="",y="")

gt = ggplot_gtable(ggplot_build(plot))
gt$widths[4] = 4*gt$widths[4]
grid.draw(gt)
```
